---
title: "Figure 3 Enriched key pathways of three omics during heart development and maturation"
output:
  html_document:
    df_print: paged
---

Library Packages
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
suppressPackageStartupMessages(library(limma)) # Bioconductor v3.48.3
suppressPackageStartupMessages(library(org.Mm.eg.db)) # Bioconductor v3.13.0 
suppressPackageStartupMessages(library(networkD3)) # CRAN v0.4

rm(list = ls(all.names = TRUE))
gc()
```

Figure 3
Define Transcriptome DEG
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
load("../SourceData/omic_data.Rds")
tmp <- mmu_heart_trs
temp_ensemble <- substr(tmp[,1],1,18)
geneinfo <- select(org.Mm.eg.db,keys = temp_ensemble,columns = c("SYMBOL"),keytype = "ENSEMBL")
geneinfo <- geneinfo[!duplicated(geneinfo[,1]),]
mmu_heart_trs <- data.frame(geneinfo,mmu_heart_trs[,2:31]);rm(tmp,temp_ensemble,geneinfo)
# Transcriptome Stage 1
count <- mmu_heart_trs[,c(1,12:20,3:11)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG1 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_trs[,c(1,21:26,3:11)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG2 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_trs[,c(1,27:32,3:11)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG3 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

nrDEG1 <- data.frame(rownames(nrDEG1),nrDEG1)
colnames(nrDEG1)[1] <- "ENSEMBL"
nrDEG2 <- data.frame(rownames(nrDEG2),nrDEG2)
colnames(nrDEG2)[1] <- "ENSEMBL"
nrDEG3 <- data.frame(rownames(nrDEG3),nrDEG3)
colnames(nrDEG3)[1] <- "ENSEMBL"

reslist <- merge(nrDEG2,nrDEG1,by="ENSEMBL")
reslist <- merge(reslist,nrDEG3,by="ENSEMBL")
# write.csv(reslist[,1],"trs_stage1.csv")

# Transcriptome Stage 2
count <- mmu_heart_trs[,c(1,3:11,12:20)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG1 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_trs[,c(1,21:26,12:20)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG2 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_trs[,c(1,27:32,12:20)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG3 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

nrDEG1 <- data.frame(rownames(nrDEG1),nrDEG1)
colnames(nrDEG1)[1] <- "ENSEMBL"
nrDEG2 <- data.frame(rownames(nrDEG2),nrDEG2)
colnames(nrDEG2)[1] <- "ENSEMBL"
nrDEG3 <- data.frame(rownames(nrDEG3),nrDEG3)
colnames(nrDEG3)[1] <- "ENSEMBL"

reslist <- merge(nrDEG2,nrDEG1,by="ENSEMBL")
reslist <- merge(reslist,nrDEG3,by="ENSEMBL")
# write.csv(reslist[,1],"trs_stage2.csv")

# Transcriptome Stage 3
count <- mmu_heart_trs[,c(1,3:11,21:26)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG1 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_trs[,c(1,12:20,21:26)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG2 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_trs[,c(1,27:32,21:26)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG3 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

nrDEG1 <- data.frame(rownames(nrDEG1),nrDEG1)
colnames(nrDEG1)[1] <- "ENSEMBL"
nrDEG2 <- data.frame(rownames(nrDEG2),nrDEG2)
colnames(nrDEG2)[1] <- "ENSEMBL"
nrDEG3 <- data.frame(rownames(nrDEG3),nrDEG3)
colnames(nrDEG3)[1] <- "ENSEMBL"

reslist <- merge(nrDEG2,nrDEG1,by="ENSEMBL")
reslist <- merge(reslist,nrDEG3,by="ENSEMBL")
# write.csv(reslist[,1],"trs_stage3.csv")

# Transcriptome Stage 4
count <- mmu_heart_trs[,c(1,3:11,27:32)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG1 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_trs[,c(1,12:20,27:32)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG2 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_trs[,c(1,21:26,27:32)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG3 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

nrDEG1 <- data.frame(rownames(nrDEG1),nrDEG1)
colnames(nrDEG1)[1] <- "ENSEMBL"
nrDEG2 <- data.frame(rownames(nrDEG2),nrDEG2)
colnames(nrDEG2)[1] <- "ENSEMBL"
nrDEG3 <- data.frame(rownames(nrDEG3),nrDEG3)
colnames(nrDEG3)[1] <- "ENSEMBL"

reslist <- merge(nrDEG2,nrDEG1,by="ENSEMBL")
reslist <- merge(reslist,nrDEG3,by="ENSEMBL")
# write.csv(reslist[,1],"trs_stage4.csv")
```

Define Proteome DEG
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
# Proteome Stage 1
count <- mmu_heart_pro[,c(1,11:19,2:10)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG1 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_pro[,c(1,20:25,2:10)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG2 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_pro[,c(1,26:31,2:10)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG3 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

nrDEG1 <- data.frame(rownames(nrDEG1),nrDEG1)
colnames(nrDEG1)[1] <- "ENSEMBL"
nrDEG2 <- data.frame(rownames(nrDEG2),nrDEG2)
colnames(nrDEG2)[1] <- "ENSEMBL"
nrDEG3 <- data.frame(rownames(nrDEG3),nrDEG3)
colnames(nrDEG3)[1] <- "ENSEMBL"

reslist <- merge(nrDEG2,nrDEG1,by="ENSEMBL")
reslist <- merge(reslist,nrDEG3,by="ENSEMBL")
temp_id <- reslist[,1]
geneinfo <- select(org.Mm.eg.db,keys=temp_id,columns=c("ENSEMBL","ENTREZID"),keytype="SYMBOL")
geneinfo <- geneinfo[!duplicated(geneinfo[,1]),]
geneinfo <- na.omit(geneinfo)
# write.csv(geneinfo,"pro_stage1.csv")

# Proteome Stage 2
count <- mmu_heart_pro[,c(1,2:10,11:19)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG1 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_pro[,c(1,20:25,11:19)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG2 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_pro[,c(1,26:31,11:19)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG3 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

nrDEG1 <- data.frame(rownames(nrDEG1),nrDEG1)
colnames(nrDEG1)[1] <- "ENSEMBL"
nrDEG2 <- data.frame(rownames(nrDEG2),nrDEG2)
colnames(nrDEG2)[1] <- "ENSEMBL"
nrDEG3 <- data.frame(rownames(nrDEG3),nrDEG3)
colnames(nrDEG3)[1] <- "ENSEMBL"

reslist <- merge(nrDEG2,nrDEG1,by="ENSEMBL")
reslist <- merge(reslist,nrDEG3,by="ENSEMBL")
temp_id <- reslist[,1]
geneinfo <- select(org.Mm.eg.db,keys=temp_id,columns=c("ENSEMBL","ENTREZID"),keytype="SYMBOL")
geneinfo <- geneinfo[!duplicated(geneinfo[,1]),]
geneinfo <- na.omit(geneinfo)
# write.csv(geneinfo,"pro_stage2.csv")

# Proteome Stage 3
count <- mmu_heart_pro[,c(1,2:10,20:25)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG1 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_pro[,c(1,11:19,20:25)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG2 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_pro[,c(1,26:31,20:25)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG3 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

nrDEG1 <- data.frame(rownames(nrDEG1),nrDEG1)
colnames(nrDEG1)[1] <- "ENSEMBL"
nrDEG2 <- data.frame(rownames(nrDEG2),nrDEG2)
colnames(nrDEG2)[1] <- "ENSEMBL"
nrDEG3 <- data.frame(rownames(nrDEG3),nrDEG3)
colnames(nrDEG3)[1] <- "ENSEMBL"

reslist <- merge(nrDEG2,nrDEG1,by="ENSEMBL")
reslist <- merge(reslist,nrDEG3,by="ENSEMBL")
temp_id <- reslist[,1]
geneinfo <- select(org.Mm.eg.db,keys=temp_id,columns=c("ENSEMBL","ENTREZID"),keytype="SYMBOL")
geneinfo <- geneinfo[!duplicated(geneinfo[,1]),]
geneinfo <- na.omit(geneinfo)
# write.csv(geneinfo,"pro_stage3.csv")

# Proteome Stage 4
count <- mmu_heart_pro[,c(1,2:10,26:31)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG1 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_pro[,c(1,11:19,26:31)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG2 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_pro[,c(1,20:25,26:31)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG3 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

nrDEG1 <- data.frame(rownames(nrDEG1),nrDEG1)
colnames(nrDEG1)[1] <- "ENSEMBL"
nrDEG2 <- data.frame(rownames(nrDEG2),nrDEG2)
colnames(nrDEG2)[1] <- "ENSEMBL"
nrDEG3 <- data.frame(rownames(nrDEG3),nrDEG3)
colnames(nrDEG3)[1] <- "ENSEMBL"

reslist <- merge(nrDEG2,nrDEG1,by="ENSEMBL")
reslist <- merge(reslist,nrDEG3,by="ENSEMBL")
temp_id <- reslist[,1]
geneinfo <- select(org.Mm.eg.db,keys=temp_id,columns=c("ENSEMBL","ENTREZID"),keytype="SYMBOL")
geneinfo <- geneinfo[!duplicated(geneinfo[,1]),]
geneinfo <- na.omit(geneinfo)
# write.csv(geneinfo,"pro_stage4.csv")
```

Define PhosphoProteome DEG
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
mmu_heart_phos_diff <- data.frame(mmu_heart_phos_raw$Unique.identifier,mmu_heart_phos[,3:32])
# PhosphoProteome Stage 1
count <- mmu_heart_phos_diff[,c(1,11:19,2:10)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG1 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_phos_diff[,c(1,20:25,2:10)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG2 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_phos_diff[,c(1,26:31,2:10)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG3 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

nrDEG1 <- data.frame(rownames(nrDEG1),nrDEG1)
colnames(nrDEG1)[1] <- "Unique.identifier"
nrDEG2 <- data.frame(rownames(nrDEG2),nrDEG2)
colnames(nrDEG2)[1] <- "Unique.identifier"
nrDEG3 <- data.frame(rownames(nrDEG3),nrDEG3)
colnames(nrDEG3)[1] <- "Unique.identifier"

reslist <- merge(nrDEG2,nrDEG1,by="Unique.identifier")
reslist <- merge(reslist,nrDEG3,by="Unique.identifier")
reslist <- merge(reslist,mmu_heart_phos_raw,by="Unique.identifier")
reslist <- data.frame(reslist$ENTREZID,reslist[,1])
# write.csv(reslist[,1],"phos_stage1.csv")

# PhosphoProteome Stage 2
count <- mmu_heart_phos_diff[,c(1,2:10,11:19)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG1 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_phos_diff[,c(1,20:25,11:19)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG2 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_phos_diff[,c(1,26:31,11:19)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",9)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG3 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

nrDEG1 <- data.frame(rownames(nrDEG1),nrDEG1)
colnames(nrDEG1)[1] <- "Unique.identifier"
nrDEG2 <- data.frame(rownames(nrDEG2),nrDEG2)
colnames(nrDEG2)[1] <- "Unique.identifier"
nrDEG3 <- data.frame(rownames(nrDEG3),nrDEG3)
colnames(nrDEG3)[1] <- "Unique.identifier"

reslist <- merge(nrDEG2,nrDEG1,by="Unique.identifier")
reslist <- merge(reslist,nrDEG3,by="Unique.identifier")
reslist <- merge(reslist,mmu_heart_phos_raw,by="Unique.identifier")
reslist <- data.frame(reslist$ENTREZID,reslist[,1])
# write.csv(reslist[,1],"phos_stage2.csv")

# PhosphoProteome Stage 3
count <- mmu_heart_phos_diff[,c(1,2:10,20:25)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG1 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_phos_diff[,c(1,11:19,20:25)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG2 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_phos_diff[,c(1,26:31,20:25)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG3 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

nrDEG1 <- data.frame(rownames(nrDEG1),nrDEG1)
colnames(nrDEG1)[1] <- "Unique.identifier"
nrDEG2 <- data.frame(rownames(nrDEG2),nrDEG2)
colnames(nrDEG2)[1] <- "Unique.identifier"
nrDEG3 <- data.frame(rownames(nrDEG3),nrDEG3)
colnames(nrDEG3)[1] <- "Unique.identifier"

reslist <- merge(nrDEG2,nrDEG1,by="Unique.identifier")
reslist <- merge(reslist,nrDEG3,by="Unique.identifier")
reslist <- merge(reslist,mmu_heart_phos_raw,by="Unique.identifier")
reslist <- data.frame(reslist$ENTREZID,reslist[,1])
# write.csv(reslist[,1],"phos_stage3.csv")

# PhosphoProteome Stage 4
count <- mmu_heart_phos_diff[,c(1,2:10,26:31)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG1 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_phos_diff[,c(1,11:19,26:31)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",9), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG2 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

count <- mmu_heart_phos_diff[,c(1,20:25,26:31)]
row.names(count) <- count[,1]
count <- count[,-1]
count <- as.matrix(count)
condition <- factor(c(rep("E",6), rep("M",6)),levels = c("E","M"))
coldata <- data.frame(row.names = colnames(count), condition)
design <- model.matrix(~ 0 + condition)
colnames(design) <- levels(condition)
rownames(design) <- colnames(count)
contrast.matrix <- makeContrasts(paste0(unique(condition),collapse = "-"),levels = design)
fit <- lmFit(count,design)
fit2 <- contrasts.fit(fit,contrast.matrix)
fit2 <- eBayes(fit2)
tempOutput <- topTable(fit2,coef = 1,n = Inf)
nrDEG <- na.omit(tempOutput) 
nrDEG3 <- nrDEG[which(nrDEG$adj.P.Val<0.05 & nrDEG$logFC< 0),]

nrDEG1 <- data.frame(rownames(nrDEG1),nrDEG1)
colnames(nrDEG1)[1] <- "Unique.identifier"
nrDEG2 <- data.frame(rownames(nrDEG2),nrDEG2)
colnames(nrDEG2)[1] <- "Unique.identifier"
nrDEG3 <- data.frame(rownames(nrDEG3),nrDEG3)
colnames(nrDEG3)[1] <- "Unique.identifier"

reslist <- merge(nrDEG2,nrDEG1,by="Unique.identifier")
reslist <- merge(reslist,nrDEG3,by="Unique.identifier")
reslist <- merge(reslist,mmu_heart_phos_raw,by="Unique.identifier")
reslist <- data.frame(reslist$ENTREZID,reslist[,1])
# write.csv(reslist[,1],"phos_stage4.csv")
```

Altogether 12 files containing DEG of 3 omics were saved for ORA in DAVID ("trs_stage1", "trs_stage2", "trs_stage3", "trs_stage4", "pro_stage1",  "pro_stage2", "pro_stage3", "pro_stage4", "phos_stage1", "phos_stage2", "phos_stage3", "phos_stage4")

FDR were arranged ascending, top 10 pathways were saved ("links1.csv", "nodes1.csv", "links2.csv", "nodes2.csv", "links3.csv", "nodes3.csv" )

Plotting
```{r echo=TRUE}
# Stage1
links <- read.csv("./Network Input/link1.csv",header = TRUE,stringsAsFactors = FALSE)
nodes <- read.csv("./Network Input/node1.csv",header = TRUE,stringsAsFactors = FALSE)
links$IDsource <- match(links$omic, nodes$Name)-1 
links$IDtarget <- match(links$pathway, nodes$Name)-1
links$group <- as.factor(c(rep("type_a",10),rep("type_b",10),rep("type_c",10)))
nodes$group <- as.factor(c(paste("path",1:20,sep = "-")))
my_color <- 'd3.scaleOrdinal() .domain(["path-1","path-2","path-3","path-4","path-5",
"path-6","path-7","path-8","path-9","path-10",
"path-11","path-12","path-13","path-14","path-15",
"path-16","path-17","path-18","path-19","path-20","type_a","type_b","type_c"]) .range(["#94BCC0","#2F596F","#CF705C","#6DB9DA","#C84238","#74618F","#F2A6A5","#649857",
  "#9978BE","#F76E5F","#F8971E","#6BBCC0","#94BCC0","#2F596F","#CF705C","#6DB9DA","#C84238","#E37E74","#4DAFBC","#28A089","#FCEAE0","#DBEDEF","#AFE2D8"])'
sankeyNetwork(Links = links, Nodes = nodes,
              Source = "IDsource", Target = "IDtarget",
              Value = "P", NodeID = "Name", fontSize = 16,
              sinksRight=FALSE,
              colourScale=my_color, LinkGroup="group", NodeGroup="group")

# Stage2&3
links <- read.csv("./Network Input/link2.csv",header = TRUE,stringsAsFactors = FALSE)
nodes <- read.csv("./Network Input/node2.csv",header = TRUE,stringsAsFactors = FALSE)
links$IDsource <- match(links$omic, nodes$Name)-1 
links$IDtarget <- match(links$pathway, nodes$Name)-1
links$group <- as.factor(c(rep("type_a",8),rep("type_b",6),rep("type_c",8)))
nodes$group <- as.factor(c(paste("path",1:25,sep = "-")))
my_color <- 'd3.scaleOrdinal() .domain(["path-1","path-2","path-3","path-4","path-5",
"path-6","path-7","path-8","path-9","path-10",
"path-11","path-12","path-13","path-14","path-15",
"path-16","path-17","path-18","path-19","path-20",
"path-21","path-22","path-23","path-24","path-25","type_a","type_b","type_c"]) .range(["#94BCC0","#2F596F","#CF705C","#6DB9DA","#C84238","#74618F","#F2A6A5","#649857",
  "#9978BE","#F76E5F","#F8971E","#6BBCC0","#94BCC0","#6DB9DA","#C84238","#74618F","#F2A6A5","#649857","#2F596F","#CF705C","#6DB9DA","#C84238","#E37E74","#4DAFBC","#28A089","#FCEAE0","#DBEDEF","#AFE2D8"])'
sankeyNetwork(Links = links, Nodes = nodes,
              Source = "IDsource", Target = "IDtarget",
              Value = "P", NodeID = "Name", fontSize = 16,
              sinksRight=FALSE,
              colourScale=my_color, LinkGroup="group", NodeGroup="group")

# Stage4
links <- read.csv("./Network Input/link3.csv",header = TRUE,stringsAsFactors = FALSE)
nodes <- read.csv("./Network Input/node3.csv",header = TRUE,stringsAsFactors = FALSE)
links$IDsource <- match(links$omic, nodes$Name)-1 
links$IDtarget <- match(links$pathway, nodes$Name)-1
links$group <- as.factor(c(rep("type_a",10),rep("type_b",10),rep("type_c",10)))
nodes$group <- as.factor(c(paste("path",1:29,sep = "-")))
my_color <- 'd3.scaleOrdinal() .domain(["path-1","path-2","path-3","path-4","path-5",
"path-6","path-7","path-8","path-9","path-10",
"path-11","path-12","path-13","path-14","path-15",
"path-16","path-17","path-18","path-19","path-20",
"path-21","path-22","path-23","path-24","path-25",
"path-26","path-27","path-28","path-29","type_a","type_b","type_c"]) .range(["#94BCC0","#2F596F","#CF705C","#6DB9DA","#C84238","#74618F","#F2A6A5","#649857","#94BCC0","#2F596F","#CF705C","#6DB9DA",
  "#9978BE","#F76E5F","#F8971E","#6BBCC0","#94BCC0","#6DB9DA","#C84238","#74618F","#F2A6A5","#649857","#2F596F","#CF705C","#6DB9DA","#C84238","#E37E74","#4DAFBC","#28A089","#FCEAE0","#DBEDEF","#AFE2D8"])'
sankeyNetwork(Links = links, Nodes = nodes,
              Source = "IDsource", Target = "IDtarget",
              Value = "P", NodeID = "Name", fontSize = 16,
              sinksRight=FALSE,
              colourScale=my_color, LinkGroup="group", NodeGroup="group")
```

